Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Add a num_obs variable to article.rnw.
Switch to using AICc instead of AIC.

	num_species <- nrow(species_dat)

	ic <- "aic" #The information criterion to use, e.g. "aic" or "aicc"
	ic_weight <- sprintf("%s_weight", ic)
	ic_name <- list(aic="AIC", aicc="AICc")[ic]

@@

To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
As a measure of parsimony, we selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
As such, we calculated the {\ic} for each model.
% DBS: Is it possible that the dataset is small enough that we should be using AICc instead?

>>>>

	num_species <- nrow(species_dat)
	num_obs <- nrow(read.table("output/design-matrix.data"))

	ic <- "aicc" #The information criterion to use, e.g. "aic" or "aicc"
	ic_weight <- sprintf("%s_weight", ic)
	ic_name <- list(aic="AIC", aicc="AICc")[ic]

@@

To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
As a measure of parsimony, we selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
Some of the models had a relatively high number of parameters compared to the number of observations (\num{\Sexpr{num_obs}} observations; up to \num{\Sexpr{num_species + num_species^2}} parameters), so we used AICc to correct for this.
As such, we calculated the {\ic} for each model.
